Constraint Programming - Inside Gecode

### 2014-05-08 paper.tex
improved introduction

\newcommand{\reffig}[1]{{figure \ref{#1}}}
\newcommand{\refeq}[1]{{(\ref{#1})}}

@@

	\section{Introduction}
	Constraint programming is a method to solve mathematical problems through the formulation of constraints, which describe the desired solution. As a formal and exact definition, like it can be found in \cite[p.~16]{handbookCP} for constraint programming, is not as helpful as an example, I would like to give you a short overview on the topic through the problem of the placement of two squares such that they do not overlap.

	\begin{figure}
		\center
		\begin{tikzpicture}
			\draw (0, 0) rectangle (1, 1);
			\node at (0, -0.3) {($x_1$, $y_1$)};
			\draw[arrows=<->] (1.2, 0) -- (1.2, 1);
			\node at (1.5, 0.5) {$d_1$};
			\draw (1.5, 1.5) rectangle(2, 2);
			\node at (1.5, 1.2) {($x_2$, $y_2$)};
			\draw[arrows=<->] (2.2, 1.5) -- (2.2, 2);
			\node at (2.5, 1.75) {$d_2$};
		\end{tikzpicture}
		\caption{two squares which should not overlap}
		\label{fig:squares}
	\end{figure}

>>>>

\newcommand{\reffig}[1]{{figure~\ref{#1}}}
\newcommand{\refeq}[1]{{(\ref{#1})}}

@@

	\section{Introduction}
	Constraint programming is a method to solve mathematical problems through the formulation of constraints, which describe the desired solution. A formal and exact definition for constraint programming can be found in \cite[p.~16]{handbookCP}. To visualize the topic better I will start with the problem of the placement of two squares such that they do not overlap.

	\begin{figure}
		\center
		\begin{tikzpicture}
			\draw (0, 0) rectangle (1, 1);
			\node at (0, -0.3) {($x_1$, $y_1$)};
			\draw[arrows=<->] (1.2, 0) -- (1.2, 1);
			\node at (1.5, 0.5) {$d_1$};
			\draw (1.5, 1.5) rectangle(2, 2);
			\node at (1.5, 1.2) {($x_2$, $y_2$)};
			\draw[arrows=<->] (2.2, 1.5) -- (2.2, 2);
			\node at (2.5, 1.75) {$d_2$};
		\end{tikzpicture}
		\caption{Two squares which should not overlap}
		\label{fig:squares}
	\end{figure}
